---
title: "Data product week 4 assignment"
author: "Nordine RAJAOUI"
date: "26/07/2020"
output:
  slidy_presentation: default
  powerpoint_presentation: default
  beamer_presentation: default
always_allow_html: yes
---


## Coursera Reproducible Pitch

This is a task for the data science coursera course about developing data products for week 4. As part of this, I have created a shiny app and deployed it on the shiny server. The link is https://nordinestatisticsaccount.shinyapps.io/kmeansexample/. The code can be found at https://github.com/Nordine67200/DataProductWeek4/.

## Overview

K-means clustering is one of the simplest and popular unsupervised machine learning algorithms. Typically, unsupervised algorithms make inferences from datasets using only input vectors without referring to known, or labelled, outcomes.
We're going to work with mtcars data.The shiny application will show you, for the numbers of centroids selected,  the clusters chosen by the kmeans method. 


## UI Code
```{r , warning=FALSE, message=FALSE, eval=FALSE}
library(shiny)
# Define UI for application that draws a histogram
shinyUI(fluidPage(
    # Application title
    titlePanel("K Means applied to mtcars data"),
    # Sidebar with a slider input for number of bins
    sidebarLayout(
        sidebarPanel(
           sliderInput("sliderKM", "Choose the number of clusters:", 2, 10, value=2)
        ),
        # Show a plot of the clusters
        mainPanel(
            plotOutput("plot1", brush = brushOpts(id="brush1"))
        )
    )
))
```

## Server Code
```{r, warning=FALSE, message=FALSE, eval=FALSE}
library(shiny)
library(miniUI)
library(factoextra)
library(tidyverse)
# Define server logic required to draw a histogram
shinyServer(function(input, output) {
    mtcars_num <- mtcars %>% 
        dplyr::select(mpg,disp:qsec) 
    mtcars_num_sc <- scale(mtcars_num)
    km.out <- reactive({
        kmeans(mtcars_num_sc,centers=input$sliderKM,nstart = 25)
        })
    output$plot1 = renderPlot({
        fviz_cluster(km.out(), mtcars_num_sc, ellipse.type = "norm")
    })
})
```